---
title: "Aggregator analysis"
author: "Online sales report"
date: "17/10/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, echo = FALSE)
options(digits = 7)
library(tinytex)
library(tidyverse)
library(rio)
library(DT)
library(data.table)
library(kableExtra)

aggr_main <- read_csv("tameeni report/arranged data.csv")



```

**Performance report**



|Average responses measured in 3 month period               |  count |Ratio    |
|-----------------------------------------------------------|--------|---------|
|number of requests                                         |27670   |100%     |
|avg number of success                                      |5651    |20%      |
|avg number of late but success                             |11545   |42%      |
|avg number of errors                                       |10473   |38%      | 
|-----------------------------------------------------------|--------|---------|



##how errors are distributed 

Below are top 5 errors showed in percentatge of total errors

```{r}
error_ = read_csv("tameeni report/error_details .csv")
error_ = as.data.table(error_)

error_ratio <- error_ %>% 
  mutate( error_percentage = `Error Count`/ 3194 ) %>%
  select(`Error Message`, error_percentage)
error_ratio = as.data.table(error_ratio)

error_ratio_ <- head(error_ratio[order(error_ratio$error_percentage,
                                 decreasing=TRUE), ], 5) 

percentage <- error_ratio_ %>% group_by(`Error Message`)
  

kable(percentage)
```






```{r  , echo = FALSE}
meanlateweek2 <- aggr_main %>%
  filter(date == "week 2") %>%
  mutate( meanlate =  mean(late_success) )

meanlateweek1 <- aggr_main %>%
  filter(date == "week 1") %>%
  mutate( meanlate =  mean(late_success) )

meanlateweek3 <- aggr_main %>%
  filter(date == "week 3") %>%
  mutate( meanlate =  mean(late_success) )


meanlateallweeks <- aggr_main %>%
    mutate( meanlate =  mean(late_success) ) %>%
  select(sample_count,meanlate)


meanerrorallweeks <- aggr_main %>%
    mutate( meanerr =  mean(Error_Response) ) %>%
  select(sample_count,meanerr)

meansuccessallweeks <- aggr_main %>%
    mutate( meansuccess =  mean(success) ) %>%
  select(sample_count,meansuccess)


meansamplecount <- aggr_main %>%
    mutate( meansample =  mean(sample_count) ) %>%
  select(sample_count, meansample)




propmeanlatesample <- merge(meanlateallweeks,meansamplecount,
                            by = "sample_count")

propmeanlatesampleall <- merge(propmeanlatesample, meansuccessallweeks,
                               by = "sample_count")

finalmeantable <- merge(propmeanlatesampleall, meanerrorallweeks,
                        by = "sample_count" )

finalmeantable <- as.data.table(finalmeantable)

finale <- finalmeantable %>%
  select( meansample, meanlate , meansuccess, meanerr   )


finaleratio <- finale %>%
    mutate(meanlateratio = meanlate/meansample,
           meanerroratio = meanerr/meansample,
           meansuccratio = meansuccess/meansample) 




```

**The first observation** 

We will  view the behavior of late but success and error reponses with 
the number of requests using the a linear model method 

```{r aggregator , echo = FALSE}


plotit <- ggplot(aggr_main , aes(x=late_success  , y= sample_count ,
                               col= Error_Response )) + geom_point() +
  geom_smooth(method = "lm") 

plotit

```

if you notice there is a relation in the model between variables , 
we will dive deeper and identify which variable is more likely to have relation with the total number of requests this to prove that the late responses are not related to connectivity but instead it is related to system processing 

**What about the late but success responses** 


```{r late_success}
aggr_main %>% 
  filter(date == "week 1") %>% 
  ggplot(aes(x = sample_count, y = late_success)) +
  geom_point() +
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  labs(title = "how late_success behave with total requests")
  
  
```


```{r success}
aggr_main %>% 
  filter(date == "week 1") %>% 
  ggplot(aes(x = sample_count, y = success )) +
  geom_point() +
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  labs(title = "how success behave with total requests")
```



##What does this tell me?

- There is an evidence that the number of requests increase when the number of late responses increase , which means that the late responses are not related  to **connectivity factor** and that we have a problem in processing the information. 
- There is an association between late but success and number of requests.
- We can use the number of requests to predict the 
late but success responses and vice versa. 










...



