---
title: "aggregator performance"
author: "Fahad BinThabit"
date: "15/10/2020"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE )
library(tidyverse)
library(rio)
library(tinytex)
library(ggplot2)
library(data.table)
library(scales)
main_ = read_csv("tameeni report/arranged data.csv")
main_ = as.data.table(main_)  

```

### We will determine the relation of errors and late response with the sample data set of aggregator acitivity 

we ploted a linear model to visualize the behavior of errors and late responses with the sample  

```{r aggregator , echo = FALSE}


plotit <- ggplot(main_ , aes(x= sample_count , y= Error_Response , col= late_success )) + geom_point() + geom_smooth(method = "lm") 

plotit

```

## error details 

over 90% of the errors are technical , thus the more we get requests the higher the errors are . 

```{r pressure, echo = FALSE}
error_ = read_csv("tameeni report/error_details .csv")
error_ = as.data.table(error_)

error_ratio <- error_ %>% 
  mutate( ratio_ = `Error Count` / 3194 ) %>%
  select(`Error Message`, ratio_)
error_ratio = as.data.table(error_ratio)

error_ratio <- head(error_ratio[order(error_ratio$ratio,
                                 decreasing=TRUE), ], 5) 

percentage <- error_ratio %>% group_by(`Error Message`) 

percentage
```

The table shows 
The top 3 errors are "Service error 43%" , "Technical error 30%" & "error in response 17%" and they sum to 
43.2% + 30.4% + 17.4% = 91%



